---
title: "Dashes to my board"
author: "B. Slangen"
date: "2/15/2021"
output:
    flexdashboard::flex_dashboard:
    theme: flatly
---

```{r setup, include=FALSE}

library(forcats)
library(flexdashboard)
library(readr)
library(lubridate)
library(ggplot2)
library(tidyverse)
library(knitr)
library(DT)
library(spotifyr)
library(compmus)
library(plotly)
knitr::opts_chunk$set(echo=FALSE)
library(grid)
library(gridExtra)

```

Latest updates {.storyboard}
=====================================================================


```{r}

circshift <- function(v, n) {
  if (n == 0) v else c(tail(v, n), head(v, -n))
}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(5, 3, 3.5, 2, 4.5, 4, 2, 4.5, 2.0, 3.5, 1.5, 4.0)
minor_key <-
  c(5.0, 2.0, 3.5, 4.5, 2.0, 4.0, 2.0, 4.5, 3.5, 2.0, 1.5, 4.0)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )
```



```{r}
Dylan_chords <-
  get_tidy_audio_analysis("6HSXNV0b4M4cLJ7ljgVVeh") %>%
  compmus_align(bars, segments) %>%
  select(bars) %>%
  unnest(bars) %>%
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "mean", norm = "manhattan"
      )
  )  


Plot1 <- Dylan_chords %>% 
  compmus_match_pitch_template(
    chord_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  )  

Dylan <- Plot1 %>%
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "Time (s)", y = "") +
  xlim(55, 85)

```

```{r}
Eric_chords <-
  get_tidy_audio_analysis("5uhvUuQciVrP0p48NqSHaq") %>%
  compmus_align(bars, segments) %>%
  select(bars) %>%
  unnest(bars) %>%
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "mean", norm = "manhattan"
      )
  )

Plot2 <- Eric_chords %>% 
  compmus_match_pitch_template(
    chord_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  )  
Ericplot <- Plot2%>%
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "Time (s)", y = "") +
  xlim(65, 105)

```

```{r}
Guns_chords <-
  get_tidy_audio_analysis("4JiEyzf0Md7KEFFGWDDdCr") %>%
  compmus_align(bars, segments) %>%
  select(bars) %>%
  unnest(bars) %>%
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "mean", norm = "manhattan"
      )
  ) %>%
  mutate(song = "Guns")

plot3 <- Guns_chords %>% 
  compmus_match_pitch_template(
    chord_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) 

Gunsplot <- plot3 %>%
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "Time (s)", y = "") +
  xlim(52, 90)

```

```{r}
combinedchords <-
  Plot1 %>%
  mutate(song = " Dylan") %>%
  bind_rows(Plot2 %>% mutate(song =  "Eric")) %>%
  bind_rows(plot3 %>% mutate(song =  "guns"))



```

### pitches

```{r} 

combinedchords %>%
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "Time (s)", y = "") +
  facet_wrap(~song, scales = "free")

```

***

Considering the differences in length and timing of the songs, the tile size of the dylan song is slightly bigger than the other ones. However between the Bob Dylan version and Eric Clapton we can observe very clear similarities in chord progression. The E flat 7 chords, Fmaj and Dminor are both very clearly visible in the graph, a little less but also clearly visible is the B flat 7 chord. When comparing it with the Guns 'n Roses version we see a little less clearly that the same chords are used, however here the Eflat 7 chords is also reoccurring. Interstingly enough the Bob Dylan version highest (represented) clear chord is A7, which we see in all three, but for the Eric clapton and Guns'n Roses version we see pattern occurence around B:7 and G#min aswell. From this we can conlude that even though these songs are very different to the ear, the chords (and keys) used are very similar.


### irrelevant

```{r}
bebop <-
  get_playlist_audio_features(
    "thesoundsofspotify",
    "55s8gstHcaCyfU47mQgLrB"
  ) %>%
  slice(1:30) %>%
  add_audio_analysis()
bigband <-
  get_playlist_audio_features(
    "thesoundsofspotify",
    "2cjIvuw4VVOQSeUAZfNiqY"
  ) %>%
  slice(1:30) %>%
  add_audio_analysis()
jazz <-
  bebop %>%
  mutate(genre = "Bebop") %>%
  bind_rows(bigband %>% mutate(genre = "Big Band"))

jazz %>%
  mutate(
    sections =
      map(
        sections,                                    # sections or segments
        summarise_at,
        vars(tempo, loudness, duration),             # features of interest
        list(section_mean = mean, section_sd = sd)   # aggregation functions
      )
  ) %>%
  unnest(sections) %>%
  ggplot(
    aes(
      x = tempo,
      y = tempo_section_sd,
      colour = genre,
      alpha = loudness
    )
  ) +
  geom_point(aes(size = duration / 60)) +
  geom_rug() +
  theme_minimal() +
  ylim(0, 5) +
  labs(
    x = "Mean Tempo (bpm)",
    y = "SD Tempo",
    colour = "Genre",
    size = "Duration (min)",
    alpha = "Volume (dBFS)"
  )
```
*** 
Some text here

### irrelevant

```{r} 

jazz <-
  bebop %>%
  mutate(genre = "Bebop") %>%
  bind_rows(bigband %>% mutate(genre = "Big Band"))
jazz %>%
  mutate(
    timbre =
      map(
        segments,
        compmus_summarise,
        timbre,
        method = "mean"
      )
  ) %>%
  select(genre, timbre) %>%
  compmus_gather_timbre() %>%
  ggplot(aes(x = basis, y = value, fill = genre)) +
  geom_violin() +
  scale_fill_viridis_d() +
  labs(x = "Spotify Timbre Coefficients", y = "", fill = "Genre")

```

*** 
Some text here

INTRO
====================================================================

### Plot tab
For my first representation I have tried to create an overview of the different versions of cover songs in my Corpus. Sadly I have had some trouble getting the artists names from Spotify which made me unable to give information about this. Even a more major issue I faced was the group_by function, which can only group songs that have the exact same title. Cover songs sadly do not always have exctly the same title. In the graph below you see an attempt to show a basic distribution of my Corpus based on the energy (x-axis) and valence (y-axis). I chose these two values to give an insight in the overal feel of a song according to spotify. With this I attempted to create a feeling of how far the feel of the cover songs was apart from the original (and possibly other covers of the same song), to give a stronger sense of the differences I attempted to draw lines between different versions of the same song. It is visble that I still struggle with correct imlementation, I seem to lose colors and visibility now I have corrected the issue with the song names.


### Wavferform tab
As you can see ive included my waveform comparisons between different versions of Knocking on heavens door. I've chosen this one, because it shows absolutely no similarity what so ever. For the Bob Dylan version this makes sense as it is significantly shorter than the other version. However, the Eric Clapton version and the Guns 'N Roses version are very similar in duration. I think this is a very interesting representation on how different the "same" songs can be. I will try to show this more with graphs in the future, as making waveform analysis for all songs is not feasible nor informative. I tried showing them in a rows overview, which is nicer, however because of the code that is shown this really messes up the overview. 


```{r include=FALSE}

Magnus_Corpus <- get_playlist_audio_features("", "61rge4nRNpMipwrZ1SojP7")
#Knocking <-
#Kids <-
#FoughttheLaw <-
#Walkthisway <-
#Higherground <-
#Shotthesherif<-

```



The messed up plot
=====================================================================
```{r}

Ordered_magnus_corpus <- Magnus_Corpus %>%
    # Arrange data frame
  group_by(track.name)
  # Reorder countries by working hours in 2006

plot <- ggplot(Ordered_magnus_corpus, aes(x = energy, y = valence, group = track.name)) +
geom_point() +
geom_path(arrow = arrow(length = unit(1.5, "mm"), type = "closed"))

ggplotly(plot)



          


```



Waveform analysis
=====================================================================

Bobby VS. Eric
-----------------------------------------------------------------------



```{r}
#Bobby
Boibby_Orginal <-
  get_tidy_audio_analysis("6HSXNV0b4M4cLJ7ljgVVeh") %>%
  select(segments) %>%
  unnest(segments) %>%
  select(start, duration, pitches)
## Eric
Ericslive <-
  get_tidy_audio_analysis("5uhvUuQciVrP0p48NqSHaq") %>%
  select(segments) %>%
  unnest(segments) %>%
  select(start, duration, pitches)

compmus_long_distance(
  Boibby_Orginal %>% mutate(pitches = map(pitches, compmus_normalise, "euclidean")),
  Ericslive %>% mutate(pitches = map(pitches, compmus_normalise, "euclidean")),
  feature = pitches,
  method = "euclidean"
) %>%
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_equal() +
  labs(x = "Bob Dylan (original)", y = "Eric Clapton (Live)") +
  theme_minimal() +
  scale_fill_viridis_c(guide = NULL)

```



Bobby VS. The Guns
-----------------------------------------------------------------------



```{r}
#Bobby
Boibby_Orginal <-
  get_tidy_audio_analysis("6HSXNV0b4M4cLJ7ljgVVeh") %>%
  select(segments) %>%
  unnest(segments) %>%
  select(start, duration, pitches)
## Theguns
Theguns <-
  get_tidy_audio_analysis("4JiEyzf0Md7KEFFGWDDdCr") %>%
  select(segments) %>%
  unnest(segments) %>%
  select(start, duration, pitches)

compmus_long_distance(
  Boibby_Orginal %>% mutate(pitches = map(pitches, compmus_normalise, "euclidean")),
  Theguns %>% mutate(pitches = map(pitches, compmus_normalise, "euclidean")),
  feature = pitches,
  method = "euclidean"
) %>%
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_equal() +
  labs(x = "Bob Dylan (original)", y = "Guns 'n Roses") +
  theme_minimal() +
  scale_fill_viridis_c(guide = NULL)

```


Eric VS. The Guns
-----------------------------------------------------------------------
```{r}
# Eric
Ericslive <-
  get_tidy_audio_analysis("5uhvUuQciVrP0p48NqSHaq") %>%
  select(segments) %>%
  unnest(segments) %>%
  select(start, duration, pitches)
## Guns
Theguns <-
  get_tidy_audio_analysis("4JiEyzf0Md7KEFFGWDDdCr") %>%
  select(segments) %>%
  unnest(segments) %>%
  select(start, duration, pitches)

compmus_long_distance(
  Ericslive %>% mutate(pitches = map(pitches, compmus_normalise, "euclidean")),
  Theguns %>% mutate(pitches = map(pitches, compmus_normalise, "euclidean")),
  feature = pitches,
  method = "euclidean"
) %>%
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_equal() +
  labs(x = "Eric Clapton (Live)", y = "Guns 'n Roses") +
  theme_minimal() +
  scale_fill_viridis_c(guide = NULL)

```






pitch and timbre {.storyboard}
=====================================================================


### Dylan

```{r dylan}
dylan <-
  get_tidy_audio_analysis('6HSXNV0b4M4cLJ7ljgVVeh') %>%
  compmus_align(bars, segments) %>%
  select(bars) %>%
  unnest(bars) %>%
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "acentre", norm = "manhattan"
      )
  ) %>%
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "mean"
      )
  )
bind_rows(
  dylan %>% 
    compmus_self_similarity(pitches, "aitchison") %>% 
    mutate(d = d / max(d), type = "Chroma"),
  dylan %>% 
    compmus_self_similarity(timbre, "euclidean") %>% 
    mutate(d = d / max(d), type = "Timbre")
) %>%
  mutate() %>% 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  facet_wrap(~type) +
  scale_fill_viridis_c(option = "E", guide = "none") +
  theme_classic() + 
  labs(x = "", y = "")
```

***
Some lines here

### Clapton


```{r clapton}
clapton <-
  get_tidy_audio_analysis("5uhvUuQciVrP0p48NqSHaq") %>%
  compmus_align(bars, segments) %>%
  select(bars) %>%
  unnest(bars) %>%
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "acentre", norm = "manhattan"
      )
  ) %>%
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "mean"
      )
  )
bind_rows(
  clapton %>% 
    compmus_self_similarity(pitches, "aitchison") %>% 
    mutate(d = d / max(d), type = "Chroma"),
  clapton %>% 
    compmus_self_similarity(timbre, "euclidean") %>% 
    mutate(d = d / max(d), type = "Timbre")
) %>%
  mutate() %>% 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  facet_wrap(~type) +
  scale_fill_viridis_c(option = "E", guide = "none") +
  theme_classic() + 
  labs(x = "", y = "")

```

***
Some text here

### Roses

```{r gunsnroses}


gunsnroses<-
  get_tidy_audio_analysis("4JiEyzf0Md7KEFFGWDDdCr") %>%
  compmus_align(bars, segments) %>%
  select(bars) %>%
  unnest(bars) %>%
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "acentre", norm = "manhattan"
      )
  ) %>%
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "mean"
      )
  )
bind_rows(
  gunsnroses %>% 
    compmus_self_similarity(pitches, "aitchison") %>% 
    mutate(d = d / max(d), type = "Chroma"),
  gunsnroses %>% 
    compmus_self_similarity(timbre, "euclidean") %>% 
    mutate(d = d / max(d), type = "Timbre")
) %>%
  mutate() %>% 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  facet_wrap(~type) +
  scale_fill_viridis_c(option = "E", guide = "none") +
  theme_classic() + 
  labs(x = "", y = "")

```

***
Some lines here

### Timbre comparison


```{r timbre, echo=FALSE}
timbredylan <- dylan %>%
  compmus_gather_timbre() %>%
  mutate(song = "dylan")

timbreclapton <- clapton %>%
  compmus_gather_timbre() %>%
  mutate(song = "clapton")

gunsnrosestimbre <-gunsnroses %>%
  compmus_gather_timbre()%>%
  mutate(song = "gunsnroses")

bind_rows(timbredylan, timbreclapton, gunsnrosestimbre) %>%
  ggplot(
    aes(
     x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  )+
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  scale_fill_viridis_c() +          
  facet_wrap((~song))
  theme_classic()
  


```

*** 
We can see a bigger magnitude for the guns n roses song in more pitches than for the other two songs. This is to be expected hwne listening to these songs. The guns n roses version has the most varriation in it, and actually sounds "biggest". The clapton verson is much more calm and steady. Where the Dylan version is actual pretty quite and steady. Which is since its much smaller length also to be expected.
